---
title: "Individual Analysis"
author: "Dario Trujano-Ochoa"
date: "5/9/2022"
output: 
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Dario Trujano-Ochoa
# individual Analysis

library(pacman)
p_load(tidyverse)
p_load(janitor)
p_load(xtable)


rm(list = ls())

load('../data/ExperienceRisk_Sessions.RData')
source('../src/functions.R')

```


# Are people consistent with their own beliefs about others?

As part of the follow-up survey, the participants were asked what was the maximum gable, and to asked what was the gamble chosen by others. 
This last decision was incentivized. 


```{r,results='asis',echo=FALSE,message=FALSE}
gamble_choices <- ExperienceRisk %>% select(Gamble.1, Gamble.2, max_exp_gamble, guess_gamble_most_chosen,CR.Payoff)

simple_diff_and_others <- ExperienceRisk %>% select(simple_diff, 
                                                    Gamble.1,
                                                    max_exp_gamble, guess_gamble_most_chosen,
                                                    CR.Payoff,
                                                    sum_correct_payoffs,
                                                    numEven_all,less_than_12_even,
                                                    mean_payoff_periods)

corstars(gamble_choices,
         result = "latex")

corstars(simple_diff_and_others,
         result = "latex")

cor(simple_diff_and_others,use = "na.or.complete")


save_correlation_matrix(gamble_choices,
                        filename = "../results/gamble_choices_corr.csv",
                        use="lower",
                        digits= 3)
print("$p < .0001^{****}, p < .001^{***}, p < .01^{**}, p < .05^{*}$")
```

The answer to the gamble with the maximum expected value is not correlated with the gamble choices.
In addition, even when this correlation is not large, the gamble chosen at the end of the experiment (Gamble.2) is correlated with all other gamble choices.
The largest correlation is between the gambles in the experiment. 
Surprisingly, the correlation between this gamble choice and the guess people made about the gamble chosen by others in the follow-up survey almost as large.

